|

### 2021-01-29 supplementary_information.Rmd
Update supplementary_information.Rmd

## Longitudinal gradients of local species richness

@@

```{r fig_s20, fig.height = 6, fig.width = 8}

@@

**Figure S20 ** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ and the number of sampling sites $N_{site}$. Positive values of % bias indicate overestimation of species richness, while negative values indicate underestimation. Different panels show results with different true species richness. The box boundaries represent 25 and 75 percentiles and the whiskers represent 5 and 95 percentiles. Dots represent individual simulation replicates.

>>>>

## Longitudinal gradient of local species richness

@@

```{r fig_s20, fig.height = 6, fig.width = 6}

@@

**Figure S20 ** Sensitivity analysis of asymptotic species richness in relation to true species richness $S_{true}$ (panels) and the number of sampling sites $N_{site}$ (x-axis). Positive values of % bias indicate an overestimation of species richness, while negative values indicate an underestimation. Different panels show results with different true species richness. The box boundaries represent 25 and 75 percentiles and the whiskers represent 5 and 95 percentiles. Dots represent individual simulation replicates.
